Are rankings of financial analysts useful to investors?

### 2015-04-13 doc/paper/paper-knitr-APS.Rnw
Submitted paper to APS with her comments on Apr.10th.

\documentclass{article}
\usepackage[printfigures]{figcaps}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\usepackage{floatpag}
%\onehalfspacing
%\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
%\pagestyle{empty}
\pagestyle{fancy}

\newcommand\myTime{\now}
\fancyhead{}
\fancyhead[CO, CE]{\texttt{-Draft-}}
\fancyhead[RO, RE]{\texttt{\today, \myTime}}
\setlength{\headheight}{2\baselineskip}
\renewcommand{\headrulewidth}{0pt}
%-------------------------------------------------------------------------

@@

test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
test.a[,'true','CONS',,] <- NA

@@

bl.results['CONS','true',,] <- NA

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
periods.array[,'CONS','true',,,] <- NA

@@

\maketitle
% You need this here, or else the first page won't have a header.
\thispagestyle{fancy}

\begin{abstract}
Several institutions issue rankings based on the accuracy of price and EPS forecasts. Given that these rankings are \textit{ex-post} they may not be able useful to investors. In this paper  we show that trading strategies based on perfect foresight and past rankings outperform a passive strategy.  In addition, we report that investors are better off following analysts that issue  accurate price targets rather that those with accurate EPS forecasts. 
%Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
\end{abstract}

@@

We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy). By doing this, we indirectly address the ongoing debate in the literature on whether analysts, when issuing the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}). For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices. Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets. \footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}

@@

We define a trading strategy as follows (figure \ref{fig:bl}):
\begin{enumerate}
\item  At the beginning of quarter $t$ for each stock $i$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);

@@

In addition to these sets,  we also create a hypothetical scenario that assumes we anticipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.  This represents the perfect foresight strategy. Therefore, it serves a performance reference point to evaluate the other trading strategies. We call this the \tr{} set.

@@

\item  the \default{}  set%-- the entire history of analysts performance:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{q:default}
\widehat{Q_{t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{t}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,i}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,i}
%\end{equation}
%\end{itemize}
\end{itemize}
where $Q_{t}$ is the analysts' expected rank-weighted stock return (eq. \ref{rankq})\footnote{The  consensus returns ($Q_{cons}$) have equal weights among the analysts, and, thus, are not included information sets. However, since views also include the confidence (\ref{eq-cv}), which is based on analysts performance, we include the consensus returns to \naive{} and \default{} information sets.}.

@@

Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[,.N,by=.(Broker,type)][,.N,by=type][,N][2]}, covering \Sexpr{q.data[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks. Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised. After one year we assume that TP recommendation expires.

@@

Given that we have two different ranking datasets (based on TP and EPS), we, further, consider S\&P500 stocks that are part of both datasets. We call this subset of stocks as the \same{} and the full set of S\&P500 stocks as the \all{}.

Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data. Panel A shows the number of quarterly target prices per stock. For the sample period (1999-2009), we report that each stock in the \same{} and the \all{} stock sets had on average of \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively, quarterly target price reports. Panel B  presents similar statistics of the number of EPS forecasts. The average number of quarterly forecasts for the  \same{} and the \all{} is \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively.

@@

Table \ref{tab:example} and figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}. Four analysts had valid target prices for Amazon for second quarter of 1999. We plot the daily Amazon price against the brokers' target prices. Table \ref{tab:example} shows the resulting TP and EPS rankings. On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate. For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.

@@

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles\footnote{For the case of the \same{} stock set, the results of ranking consistency are similar to that of the \all{} stock set.}.

In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year) in the \all{} stock set respectively.

@@

Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). As mentioned above (sec. \ref{inf-set}), the consensus views have equal weights among the analysts; thus, for the case of \tr{} they are not existent and for cases of the \naive{} and the \default{}, they are equal as we use the last known $Q_{cons}$ (eq. \ref{consq}). Therefore, the average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets for the \all{} stock set is \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\% and for the \same{} stock set is \Sexpr{test.a['Total',,'CONS','mean','same'][[2]]*100 }\%

Panel B of the table shows the TP accuracy weighted average expected returns for the \all{} stock sets (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%) and for the \same{} (\Sexpr{test.a['Total',,'PT','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','same'][[3]]*100}\%)

Panel C shows the EPS based weighted expected returns averages for the \all{} set (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%) and for the \same{} stock set (\Sexpr{test.a['Total',,'EPS','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','same'][[3]]*100}\%)

Overall compared to the consensus the ranked weighted expected returns (``smart estimates") are less optimistic. The \default{} information set shows the lowest values of expected returns among all information sets. For the different stock sets,  the \same{} set of stocks has higher values of expected returns compared to the \all{} stocks.

@@

We report the results from different trading strategies in table (\ref{tab:strategy}). We split the table into four panels. Panel A shows  the performance for  the passive (market) strategy \textit{Market}. Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategies for each of the information availability sets.

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock set: \Sexpr{bl.results['TP',1,1,'all']}\% and  \Sexpr{bl.results['EPS',1,1,'all']}\% and, respectively, for the \same{} set of stocks: \Sexpr{bl.results['TP',1,1,'same']}\% and \Sexpr{bl.results['EPS',1,1,'same']}\%. All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio for the \all{} (\same{}) stock set is \Sexpr{ bl.results['TP',1,'ann.sr','all']} (\Sexpr{ bl.results['TP',1,'ann.sr','same']}) against \Sexpr{ bl.results['EPS',1,'ann.sr','all']} (\Sexpr{ bl.results['EPS',1,'ann.sr','same']}), and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for  the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set. The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,1]}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) set of stocks of \Sexpr{bl.results['TP',2,1,sets[1]]}\% (\Sexpr{bl.results['TP',2,1,sets[2]]}\%) and  \Sexpr{bl.results['CONS',2,1,sets[1]]}\% (\Sexpr{bl.results['CONS',2,1,sets[2]]}\%) respectively. The active strategy based on EPS forecasts, demonstrated negative annualized cumulative returns in both sets of stocks of  \Sexpr{bl.results['EPS',2,1,sets[1]]}\% and \Sexpr{bl.results['EPS',2,1,sets[2]]}\% for the \all{} and the \same{} respectively.

The risk-adjusted results for this information sets shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy with Sharpe ratios for the \all{} stocks of \Sexpr{ bl.results['TP',2,'ann.sr',sets[1]]} and for the \same{} of \Sexpr{ bl.results['TP',2,'ann.sr',sets[2]]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[1]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[1]]} respectively for the \all{} set  and  of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[2]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[2]]} respectively for the \same{} set of stocks. The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods independent of stock sets.

Panel D of table \ref{tab:strategy} demonstrates an interesting finding. On one hand, when consider \all{} set of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (\Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies). On the other hand, the result changes when consider \same{} set of stocks (\Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).

The analysis of the sub-periods performance of \textit{TP} and \textit{EPS} depicted in table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4 of \Sexpr{periods.array[1,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[1,'TP',3,2,1,1]*100}\%  in 2001Q1/2005Q4 of \Sexpr{periods.array[2,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[2,'TP',3,2,1,1]*100}\% respectively for the \textit{EPS} and \textit{TP}. For the rest  sup-periods, the annualized cumulative returns of the \textit{EPS} strategy have been constantly lower than that of the \textit{TP} strategy. This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s. Table \ref{tab:substrategy-same} shows the sub-period results when considered only the \same{} set of stock. In this setting, the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} in every sup-period.

@@

Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that good at forecasting EPS.  This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not based upon the simple valuation models.

>>>>

\documentclass{article}
%\usepackage[printfigures]{figcaps}
\usepackage[nolists,tablesfirst,nomarkers]{endfloat}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\usepackage{floatpag}
%\onehalfspacing
%\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
%%\pagestyle{empty}
%\pagestyle{fancy}

% \newcommand\myTime{\now}
% \fancyhead{}
% \fancyhead[CO, CE]{\texttt{-Draft-}}
% \fancyhead[RO, RE]{\texttt{\today, \myTime}}
% \setlength{\headheight}{2\baselineskip}
% \renewcommand{\headrulewidth}{0pt}
%-------------------------------------------------------------------------

@@

test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
#test.a[,'true','CONS',,] <- NA

@@

#bl.results['CONS','true',,] <- NA

@@

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
#periods.array[,'CONS','true',,,] <- NA

@@

\maketitle
% You need this here, or else the first page won't have a header.
%\thispagestyle{fancy}

\begin{abstract}
Several institutions issue rankings based on the accuracy of price and EPS forecasts. Given that these rankings are \textit{ex-post} they may not be useful to investors. In this paper  we show that trading strategies based on perfect foresight and past rankings outperform a passive strategy.  In addition, we report that investors are better off following analysts that issue  accurate price targets rather that those with accurate EPS forecasts. 
%Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
\end{abstract}

@@

We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy). By doing this, we indirectly address the ongoing debate in the literature on whether analysts, when issuing the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}). For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices. Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets\footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}.

@@

We define a trading strategy as follows (Figure \ref{fig:bl}):
\begin{enumerate}
\item  At the beginning of quarter $t$ for each stock $i$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);

@@

In addition to these sets,  we also create a hypothetical scenario that assumes we anticipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.  This represents the perfect foresight strategy. The perfect foresight refers to analyst rankings not stock prices. Therefore, it serves a performance reference point to evaluate the other trading strategies. We call this the \tr{} set.

@@

\item  the \default{}  set%-- the entire history of analysts performance:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{q:default}
\widehat{Q_{t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{t}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,i}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,i}
%\end{equation}
%\end{itemize}
\end{itemize}
where $Q_{t}$ is the analysts' expected rank-weighted stock return (eq. \ref{rankq})

@@

Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[,.N,by=.(Broker,type)][,.N,by=type][,N][2]}, covering \Sexpr{q.data[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks. Given the fact that financial analysts commonly issue TP with the one year horizon\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised. After one year we assume that TP recommendation expires.

@@

Given that we have two different ranking datasets (based on TP and EPS), we, further, consider S\&P500 stocks that are part of both datasets. We call this sample of stocks as the \same{} and the full sample of S\&P500 stocks as the \all{}.

Table \ref{tab:ret-stat} shows the distribution of the final sample of target price and EPS data. Panel A shows the number of quarterly target prices per stock. For the sample period (1999-2009), we report that each stock in the \same{} and the \all{} stock sets had on average of \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively, quarterly target price reports. Panel B  presents similar statistics of the number of EPS forecasts. The average number of quarterly forecasts for the  \same{} and the \all{} is \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively.

@@

Table \ref{tab:example} and Figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}. Four analysts had valid target prices for Amazon for second quarter of 1999. We plot the daily Amazon price against the brokers' target prices. Table \ref{tab:example} shows the resulting TP and EPS rankings. On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate. For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.

@@

Table \ref{tab:rank-stat} shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles\footnote{For the case of the \same{} stock sample, the results of ranking consistency analysis are similar.}.

In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles, respectively,  after one quarter (year) in the \all{} stock samples.

@@

Table \ref{tab:view-stat} presents the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).

@@

Panel A of Table \ref{tab:view-stat} show the statistics for the consensus expectations as defined in eq. (\ref{consq}). As mentioned above (sec. \ref{inf-set}), the consensus views have equal weights among the analysts, regardless of their ranks; thus, for the case of \tr{}, \naive{}, and \default{, the mean is the same regardless of knowing or not the present or past rankings ($Q_{cons}$ (eq. \ref{consq})). As such, the mean, median, and standard deviation in the \tr{}, \naive{}, and \default{} information sets are the same. For the sample of \all{} stocks the mean expected return is \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%. However, since views also include the confidence (eq. \ref{eq-cv}), which is based on analysts past performance, the results of the trading strategy based on consensus expectations will be different for the \naive{} and \default{} information sets.

%and for the \same{} sample of stocks the mean is \Sexpr{test.a['Total',,'CONS','mean','same'][[2]]*100 }\%.

Panel B of the table shows the TP accuracy weighted average expected returns. For the sample of \all{} stocks the weighted average returns for \tr{}, \naive{}, and \default{} information sets are respectively \Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%.

%and for the \same{} (\Sexpr{test.a['Total',,'PT','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','same'][[3]]*100}\%)

Panel C shows the EPS based weighted expected return. The average return for the \tr{}, \naive{}, and \default{} information sets are respectively \Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%.

The statistics for the subsample of stocks that integrate both the TP of the EPS samples are similar.

%and for the \same{} stock sample (\Sexpr{test.a['Total',,'EPS','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','same'][[3]]*100}\%)

Overall compared to the consensus the ranked weighted expected returns (``smart estimates") are less optimistic. The \default{} information set shows the lowest values of expected returns among all information sets. For the different stock sets,  the \same{} sample of stocks has higher values of expected returns compared to the \all{} stocks.

@@

We report the results from different trading strategies in Table \ref{tab:strategy}. We split the table into four panels. Panel A shows  the performance for  the passive (market) strategy \textit{Market}. Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategies for each of the information availability sets.

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock sample: \Sexpr{bl.results['TP',1,1,'all']}\% and  \Sexpr{bl.results['EPS',1,1,'all']}\%. For the \same{} sample of stocks these are respectively \Sexpr{bl.results['TP',1,1,'same']}\% and \Sexpr{bl.results['EPS',1,1,'same']}\%. The two smart strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).  The consensus strategy annualized returns for the \all{} and the \same{} sample of stocks are respectively   \Sexpr{bl.results['CONS',1,1,'all']}\% and  \Sexpr{bl.results['CONS',1,1,'same']}\%

The results show, as expected, that  investors would better off if they knew in advance who the top analysts in terms of TP or EPS accuracy would be. In any case, the results suggest that the advices of analysts, as a group, are valuable. 
%Yet the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio for the \all{} (\same{}) stock sample is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for  the \textit{EPS}, \textit{CONS} and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the shorter trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period. The results for the subsample of stocks that integrate both the TP of the EPS datasets are similar.

@@

\subsection{Feasible strategies}
Panel C of Table \ref{tab:strategy} shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set. We report the results of forming portfolios with the available stocks within each dataset (\all{}) and the subsample of stocks that include both the TP or the EPS datasets (\same{}).

The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,1]}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) sample of stocks of \Sexpr{bl.results['TP',2,1,sets[1]]}\% (\Sexpr{bl.results['TP',2,1,sets[2]]}\%) and  \Sexpr{bl.results['CONS',2,1,sets[1]]}\% (\Sexpr{bl.results['CONS',2,1,sets[2]]}\%) respectively. The active strategy based on EPS forecasts, has negative annualized cumulative returns of  \Sexpr{bl.results['EPS',2,1,sets[1]]}\% and \Sexpr{bl.results['EPS',2,1,sets[2]]}\% for the \all{} and the \same{} samples respectively.

The risk-adjusted results for this information set shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy regardless of forming portfolios with \all{} stocks or with the \same{} subsample. 
%Sharpe ratios for the \all{} stocks of \Sexpr{ bl.results['TP',2,'ann.sr',sets[1]]} and for the \same{} of \Sexpr{ bl.results['TP',2,'ann.sr',sets[2]]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[1]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[1]]} respectively for the \all{} sample  and  of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[2]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[2]]} respectively for the \same{} sample of stocks. 
The results in panel B of Table \ref{tab:substrategy} show as well that this strategy outperforms the others for all of the shorter trading periods.

Panel D of Table \ref{tab:strategy} shows interesting and slightly different findings. On one hand, when all the analyst forecast performance track record is included to set the rankings, we observe an increase in annualized cumulative returns and risk-adjusted returns for the smart strategies. Particularly in the case of the EPS strategy, the results suggest that strategies that weight the estimates with accuracy rankings obtained using more information show better performance: when we consider the \all{} sample of stocks, the strategy based on the accuracy of EPS forecasts outperforms the other strategies (annualized cumulative returns of \Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS}). The TP strategy dominates when we consider the subsample of stocks that are included in both the TP and EPS datasets (\Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\% respectively for the \textit{EPS}, \textit{TP} and \textit{CONS} strategies) but the returns and risk-adjusted improve as well when compared to the figures in Panel C.

%On one hand, when consider \all{} sample of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (\Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies). On the other hand, the result changes when consider \same{} sample of stocks (\Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).

The analysis of the sub-periods performance of the \textit{TP} and \textit{EPS} -based strategies depicted in Table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4  \Sexpr{periods.array[1,'EPS',3,2,1,1]*100}\% vs. \Sexpr{periods.array[1,'TP',3,2,1,1]*100}\%  in 2001Q1/2005Q4 \Sexpr{periods.array[2,'EPS',3,2,1,1]*100}\%  vs. \Sexpr{periods.array[2,'TP',3,2,1,1]*100}\% respectively for the \textit{EPS} and the \textit{TP} strategies. For the all the other sup-periods, the annualized cumulative returns of the \textit{EPS} strategy are lower than those of the \textit{TP} strategy. 
%This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s. 
Table \ref{tab:substrategy-same} shows the sub-period results when we consider only the sample of stocks that integrates the TP and EPS dataset. In this setting (\same{}), the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} strategies in every sub-period.

@@

Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that are good at forecasting EPS.  This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that stock recommendations of the most accurate analysts are not based upon simple valuation models.
